### 2016-04-19 text/ms.Rmd
Start editing discussion and removing comments

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [x] add back in the roc plot and sentence in the main text
- [ ] rerun the main simulation analysis because the equations of change for the slope
- [ ] manually adjusted the labels in figure 4
- [ ] update the magic number get inserted to use the equation that only has the basic model
-->

@@

<!-- TODO PE .... mean or slope of b/bmsy: Dan: logged or normal space? For the
status regression where you are estimating log(B/Bmsy), wouldn't you need to
correct for the retransformation bias in the estimating median proportional
error later down? I could be missing something though in whether that applied
once you've calculated proportional error-->

@@

<!--> TODO update the result numbers to report the models that don't have the covariates -->

@@

Ensemble methods provide a useful approach to situations where conservation and
environmental resource management decisions must be made on the basis of
multiple, potentially contrasting estimates of status --- a situation common to
many settings beyond fisheries. Compared to individual models of fish population
status, ensemble methods were consistently the best or among the best across
three performance dimensions (accuracy, bias, and rank-order correlation), two
response variables (status and trend), two datasets (simulated and global
fisheries), and multiple ensemble methods (from a simple average to machine
learning superensembles). Our results suggest choosing a superensemble model
that allows for non-parametric relationships, such as machine learning methods.
These methods provide added insight into individual model behavior and generally
performed the best; however, even a simple average of predictions across
multiple models may provide a more useful measure of the desired parameter than
a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. Such individual models would
be expected to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each <!-- is this only true for
superensembles?-->. Second, ensemble models will be most effective when they are
not overfit to the training dataset. Cross-validation testing [@caruana2004;
@hastie2009] and methods that are robust to overfitting such as random forests
[@breiman2001], may help avoid overfitting ensemble models. We note that our
simplest ensemble model, an average of individual model predictions, performed
approximately as well as complex machine learning models when we trained our
superensembles on the simulation dataset and tested them on a separate 'real'
dataset (i.e. the RAM Legacy Stock Assessment database, Fig.
\ref{performance}b). Third, ensemble models will be most effective when they are
trained on data that are representative of the dataset of interest [@knutti2009;
@weigel2010]. Cross-validation within a training dataset will provide an
optimistically biased impression of predictive performance if the training
dataset fundamentally differs from the dataset of interest [@hastie2009].

>>>>

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [x] add back in the roc plot and sentence in the main text
- [ ] rerun the main simulation analysis because the equations of change for the slope
- [ ] manually adjusted the labels in figure 4
- [x] update the magic number get inserted to use the equation that only has the basic model
-->

@@

@@

@@

Ensemble methods provide a useful approach to situations where environmental
resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status. Compared to individual models of
fish population status, ensemble methods were consistently the best or among
the best across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trend), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a simple
average to machine learning superensembles). Our results suggest choosing a
superensemble model that allows for non-parametric relationships, such as
machine learning methods. These methods provide added insight into individual
model behavior and generally performed the best; however, even a simple average
of predictions across multiple models may provide a more useful measure of the
desired parameter than a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. Such individual models would
be expected to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each superensembles? Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate 'real' dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].
